---
title: "Midterm Code Report: NYT Surveillance Corpus Analysis"
subtitle: "SIS/ITEC 724 — Spring 2026 — Professor Cogburn"
author: "Daniel Chavez"
date: today
format:
  pdf:
    titlepage: true
    toc: true
    toc-depth: 2
execute:
  echo: true
  warning: false
  message: false
editor: source
---
```{r}
#| label: setup
#| echo: false
library(reticulate)
# use_condaenv("/Users/chavez/miniconda3/envs/YOURENV", required = TRUE)
```

# CRISP-DM Step 1: Business/Research Understanding

# Project Overview

# Longitudinal analysis of NYT surveillance coverage (1995–2025),
# comparing U.S. and PRC government surveillance framing across ~13,000 articles.
# Data exported from ProQuest TDM Studio as two CSV files.

# Disaggregated Research Questions (per Assignment 6 feedback):
#
# RQ1: Longitudinal sentiment trends
#   RQ1.1: What is the overall trajectory of sentiment toward government
#          surveillance in NYT coverage from 1995–2025? (Bing lexicon, loess trend)
#   RQ1.2: Do VADER scores converge with dictionary-based results,
#          validating the trend? (VADER triangulation)
#
# RQ2: Dominant frames and themes
#   RQ2.1: What are the most frequent terms and bigrams characterizing
#          surveillance coverage? (word freq, n-grams, TF-IDF — inductive/MVP core)
#   RQ2.2: What latent topics emerge from LDA modeling, and how do topic
#          proportions shift across eras? (LDA — elective extension)
#   RQ2.3: What emotional frames (NRC emotions) dominate coverage? (NRC lexicon)
#
# RQ3: U.S. vs. PRC framing differences
#   RQ3.1: Which words statistically distinguish U.S. from PRC coverage?
#          (quanteda keyness/chi-squared — elective extension)
#   RQ3.2: How do sentiment trajectories differ between the two corpora?
#          (comparative sentiment — MVP core deductive)
#   RQ3.3: Does the semantic neighborhood of "surveillance" differ across
#          corpora? (GloVe + Word2Vec embeddings — elective extension)
#
# RQ4: Event-driven shifts
#   RQ4.1: How did publication volume and sentiment shift around 9/11 (2001)
#          and the Snowden revelations (2013)? (event-window analysis)
#   RQ4.2: How did the emergence of AI-enabled surveillance (~2017) correspond
#          with changes in vocabulary and tone? (keyword tracking, embeddings)

# CRISP-DM Step 2: Data Understanding & Collection

# Part 1: Environment Setup
# ---------------------------------------------------------------
# Loads R packages across three text mining ecosystems (tm, tidytext,
# quanteda) plus visualization, embeddings, and Python bridge.

## Deliverable 1: Install R Packages
```{r}
#| label: install-r-packages
#| eval: false

install.packages(c("tidytext", "tm", "quanteda", "quanteda.textplots",
                    "quanteda.textstats", "tidyverse", "scales",
                    "textdata", "topicmodels", "text2vec"))
```

## Deliverable 2: Load R Libraries
```{r}
#| label: load-r-libraries

library(tidyverse)
library(tidytext)
library(tm)
library(quanteda)
library(quanteda.textplots)
library(quanteda.textstats)
library(scales)
```

## Deliverable 3: Verify Python Environment
```{r}
#| label: check-python
reticulate::py_config()
```
```{python}
#| label: python-imports

import numpy as np
import warnings
warnings.filterwarnings('ignore')

import nltk
nltk.download("stopwords", quiet=True)
nltk.download("punkt", quiet=True)
nltk.download("punkt_tab", quiet=True)
nltk.download("vader_lexicon", quiet=True)

from nltk.corpus import stopwords
from nltk.sentiment.vader import SentimentIntensityAnalyzer

print("Python environment verified successfully.")
print(f"NumPy version: {np.__version__}")
```

# Part 2: Data Import
# ---------------------------------------------------------------
# Data exported from ProQuest TDM Studio as two CSV files stored
# in the Data/ subdirectory. Each row = one article with full text
# and metadata. Combined into a single dataframe with corpus tag
# and four analytical eras defined in the conceptual framework.
# Corpus: ~7,621 U.S. articles + ~5,391 PRC articles = ~13,012 total.

## Deliverable 4: Load CSV Data

# Reads both CSVs, tags corpus of origin, combines, and creates
# year and era variables. Column names may need adjustment after
# inspecting actual CSV headers — check with head() or colnames().
```{r}
#| label: load-data

us_raw  <- read_csv("Data/NYT US Sentiment.csv", show_col_types = FALSE)
prc_raw <- read_csv("Data/NYT China Sentiment extended.csv", show_col_types = FALSE)

# Tag corpus of origin
us_raw$corpus  <- "US"
prc_raw$corpus <- "PRC"

# Combine and build text field from Title + Subject Terms
# Date column is already parsed as date type by read_csv
sample_corpus <- bind_rows(us_raw, prc_raw) %>%
  mutate(
    doc_id   = paste0(corpus, "_", GOID),
    pub_date = Date,
    year     = year(pub_date),
    # Combine Title + Subject Terms into a single text field
    # Subject Terms arrive as "['term1', 'term2']" — clean the brackets/quotes
    clean_subjects = str_remove_all(`Subject Terms`, "\\[|\\]|'"),
    fulltext = paste(Title, clean_subjects, sep = " "),
    fulltext = str_squish(fulltext),
    era = case_when(
      year < 2001 ~ "Pre-9/11",
      year >= 2001 & year < 2013 ~ "Post-9/11",
      year >= 2013 & year < 2017 ~ "Post-Snowden",
      year >= 2017 ~ "AI Era"
    ),
    era = factor(era, levels = c("Pre-9/11", "Post-9/11", "Post-Snowden", "AI Era"))
  ) %>%
  filter(!is.na(fulltext), fulltext != "")

cat(sprintf("Combined corpus: %d documents (%d US, %d PRC)\n",
            nrow(sample_corpus),
            sum(sample_corpus$corpus == "US"),
            sum(sample_corpus$corpus == "PRC")))
cat(sprintf("Year range: %d – %d\n", min(sample_corpus$year), max(sample_corpus$year)))
```

# CRISP-DM Step 3: Data Preparation

# Part 3: Preprocessing
# ---------------------------------------------------------------
# Tokenization, stopword removal, custom surveillance-specific
# stopword dictionary. All downstream analyses depend on this step.

## Deliverable 5: Tokenize and Remove Stopwords

# Breaks articles into unigrams. Removes standard English stopwords
# plus custom list of high-frequency NYT noise terms.
# Filters to alphabetic tokens, 2+ characters.
# Supports: all RQs.
```{r}
#| label: tokenize

custom_stops <- tibble(word = c("said", "new", "york", "times", "mr", "ms",
                                "also", "would", "could", "one", "two",
                                "like", "just", "even", "say", "says",
                                "article", "percent", "year", "years"))

tokens <- sample_corpus %>%
  unnest_tokens(word, fulltext) %>%
  anti_join(stop_words, by = "word") %>%
  anti_join(custom_stops, by = "word") %>%
  filter(str_detect(word, "^[a-z]{2,}$"))

cat(sprintf("Total tokens after preprocessing: %s\n", comma(nrow(tokens))))
cat(sprintf("Unique vocabulary: %s terms\n", comma(n_distinct(tokens$word))))
```

# CRISP-DM Step 4: Modeling

# Part 4: Inductive Analysis — MVP Core (RQ2.1)
# ---------------------------------------------------------------

## Deliverable 6: Word Frequencies

# Answers RQ2.1 — dominant vocabulary per corpus.
# Technique: unigram frequency counts grouped by corpus.
# Viz: horizontal bar chart, faceted US vs. PRC, top 15 terms.
```{r}
#| label: word-freq

word_counts <- tokens %>%
  count(corpus, word, sort = TRUE)

top_words <- word_counts %>%
  group_by(corpus) %>%
  slice_max(n, n = 15) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, n, corpus))

ggplot(top_words, aes(x = n, y = word, fill = corpus)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ corpus, scales = "free_y") +
  scale_y_reordered() +
  scale_fill_manual(values = c("US" = "#2166AC", "PRC" = "#B2182B")) +
  labs(title = "Top 15 Most Frequent Words by Corpus",
       subtitle = "After stopword removal | NYT Surveillance Corpus",
       x = "Frequency", y = NULL) +
  theme_minimal(base_size = 11)
```

## Deliverable 7: Bigram Analysis

# Answers RQ2.1 — multi-word frames (e.g., "facial recognition,"
# "social credit," "national security").
# Technique: bigram tokenization, stopword filter on both positions.
# Viz: faceted bar chart, top 10 bigrams per corpus.
```{r}
#| label: bigrams

bigrams <- sample_corpus %>%
  unnest_tokens(bigram, fulltext, token = "ngrams", n = 2) %>%
  separate(bigram, into = c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% stop_words$word,
         !word2 %in% stop_words$word,
         !word1 %in% custom_stops$word,
         !word2 %in% custom_stops$word) %>%
  unite(bigram, word1, word2, sep = " ")

top_bigrams <- bigrams %>%
  count(corpus, bigram, sort = TRUE) %>%
  group_by(corpus) %>%
  slice_max(n, n = 10) %>%
  ungroup() %>%
  mutate(bigram = reorder_within(bigram, n, corpus))

ggplot(top_bigrams, aes(x = n, y = bigram, fill = corpus)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ corpus, scales = "free_y") +
  scale_y_reordered() +
  scale_fill_manual(values = c("US" = "#2166AC", "PRC" = "#B2182B")) +
  labs(title = "Top 10 Bigrams by Corpus",
       subtitle = "Two-word phrases reveal dominant surveillance frames",
       x = "Frequency", y = NULL) +
  theme_minimal(base_size = 11)
```

## Deliverable 8: TF-IDF Analysis

# Answers RQ2.1, bridges to RQ3.1 — distinctively important words
# per corpus (not just frequent). Down-weights common terms.
# Technique: bind_tf_idf() on corpus-level word counts.
# Viz: faceted bar chart, top 10 TF-IDF terms per corpus.
```{r}
#| label: tf-idf

corpus_tfidf <- tokens %>%
  count(corpus, word) %>%
  bind_tf_idf(word, corpus, n) %>%
  arrange(desc(tf_idf))

top_tfidf <- corpus_tfidf %>%
  group_by(corpus) %>%
  slice_max(tf_idf, n = 10) %>%
  ungroup() %>%
  mutate(word = reorder_within(word, tf_idf, corpus))

ggplot(top_tfidf, aes(x = tf_idf, y = word, fill = corpus)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ corpus, scales = "free_y") +
  scale_y_reordered() +
  scale_fill_manual(values = c("US" = "#2166AC", "PRC" = "#B2182B")) +
  labs(title = "Top TF-IDF Terms by Corpus",
       subtitle = "Words that most distinguish U.S. from PRC coverage",
       x = "TF-IDF Score", y = NULL) +
  theme_minimal(base_size = 11)
```

# Part 5: Deductive Analysis — MVP Core (RQ1, RQ3.2)
# ---------------------------------------------------------------

## Deliverable 9: Bing Lexicon Sentiment Scoring

# Answers RQ1.1 and RQ3.2 — binary pos/neg via Bing lexicon.
# Computes article-level net sentiment and ratio.
# Wrangling: inner_join with Bing, pivot wide, compute scores.
# Note: Bing is binary; no intensity or negation handling.
```{r}
#| label: bing-sentiment

bing <- get_sentiments("bing")

sentiment_by_article <- tokens %>%
  inner_join(bing, by = "word") %>%
  count(doc_id, corpus, year, era, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>%
  mutate(net_sentiment = positive - negative,
         total_words = positive + negative,
         sentiment_ratio = net_sentiment / total_words)

cat(sprintf("Articles with sentiment data: %d of %d\n",
            n_distinct(sentiment_by_article$doc_id),
            nrow(sample_corpus)))
```

## Deliverable 10: Longitudinal Sentiment Trend (RQ1.1)

# Mean net sentiment per year, smoothed via loess.
# Viz: scatter + loess by corpus, vertical lines at 9/11, Snowden, AI era.
# Point size = article count; sparse years have wider CIs.
```{r}
#| label: sentiment-trend

yearly_sentiment <- sentiment_by_article %>%
  group_by(year, corpus) %>%
  summarize(
    mean_sentiment = mean(sentiment_ratio, na.rm = TRUE),
    n_articles = n(),
    .groups = "drop"
  )

ggplot(yearly_sentiment, aes(x = year, y = mean_sentiment, color = corpus)) +
  geom_point(aes(size = n_articles), alpha = 0.5) +
  geom_smooth(method = "loess", se = TRUE, span = 0.5) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_vline(xintercept = c(2001, 2013, 2017), linetype = "dotted",
             color = "gray40", linewidth = 0.5) +
  ggplot2::annotate("text", x = 2001, y = max(yearly_sentiment$mean_sentiment, na.rm = TRUE),
           label = "9/11", hjust = -0.2, size = 3) +
  ggplot2::annotate("text", x = 2013, y = max(yearly_sentiment$mean_sentiment, na.rm = TRUE),
           label = "Snowden", hjust = -0.2, size = 3) +
  ggplot2::annotate("text", x = 2017, y = max(yearly_sentiment$mean_sentiment, na.rm = TRUE),
           label = "AI Era", hjust = -0.2, size = 3) +
  scale_color_manual(values = c("US" = "#2166AC", "PRC" = "#B2182B")) +
  labs(title = "Longitudinal Sentiment Trends (RQ1.1)",
       subtitle = "Bing lexicon | Dotted lines mark key inflection points",
       x = "Year", y = "Mean Net Sentiment Ratio",
       color = "Corpus", size = "N Articles") +
  theme_minimal(base_size = 11)
```

## Deliverable 11: Sentiment by Era (RQ3.2, RQ4.1)

# Compares mean sentiment between US and PRC across four eras.
# Viz: grouped bar chart with standard error bars.
```{r}
#| label: sentiment-era

era_sentiment <- sentiment_by_article %>%
  group_by(era, corpus) %>%
  summarize(
    mean_sentiment = mean(sentiment_ratio, na.rm = TRUE),
    sd_sentiment   = sd(sentiment_ratio, na.rm = TRUE),
    n = n(),
    .groups = "drop"
  )

ggplot(era_sentiment, aes(x = era, y = mean_sentiment, fill = corpus)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6) +
  geom_errorbar(
    aes(ymin = mean_sentiment - sd_sentiment / sqrt(n),
        ymax = mean_sentiment + sd_sentiment / sqrt(n)),
    position = position_dodge(width = 0.7), width = 0.2
  ) +
  scale_fill_manual(values = c("US" = "#2166AC", "PRC" = "#B2182B")) +
  labs(title = "Mean Sentiment by Era and Corpus (RQ3.2, RQ4.1)",
       subtitle = "Error bars show standard error of the mean",
       x = NULL, y = "Mean Net Sentiment Ratio", fill = "Corpus") +
  theme_minimal(base_size = 11)
```

## Deliverable 12: VADER Sentiment in Python (RQ1.2)

# Triangulates Bing with VADER compound scores.
# VADER handles negation and intensifiers better than unigram lexicons.
# Convergence between Bing and VADER strengthens RQ1 findings.
```{python}
#| label: vader-sentiment

import pandas as pd
from nltk.sentiment.vader import SentimentIntensityAnalyzer

sid = SentimentIntensityAnalyzer()
corpus_data = pd.DataFrame(r.sample_corpus)

vader_scores = []
for idx, row in corpus_data.iterrows():
    scores = sid.polarity_scores(str(row['fulltext']))
    vader_scores.append({
        'doc_id':   row['doc_id'],
        'corpus':   row['corpus'],
        'year':     int(row['year']),
        'compound': scores['compound'],
        'pos':      scores['pos'],
        'neg':      scores['neg'],
        'neu':      scores['neu']
    })

print(f"VADER scored {len(vader_scores)} documents.")
print(f"Mean compound (US):  {sum(s['compound'] for s in vader_scores if s['corpus']=='US') / max(1, sum(1 for s in vader_scores if s['corpus']=='US')):.3f}")
print(f"Mean compound (PRC): {sum(s['compound'] for s in vader_scores if s['corpus']=='PRC') / max(1, sum(1 for s in vader_scores if s['corpus']=='PRC')):.3f}")
```
```{r}
#| label: vader-to-r

vader_df <- py$vader_scores %>%
  bind_rows() %>%
  mutate(year = as.integer(year))

vader_yearly <- vader_df %>%
  group_by(year, corpus) %>%
  summarize(mean_compound = mean(compound, na.rm = TRUE),
            n = n(), .groups = "drop")

ggplot(vader_yearly, aes(x = year, y = mean_compound, color = corpus)) +
  geom_point(aes(size = n), alpha = 0.5) +
  geom_smooth(method = "loess", se = TRUE, span = 0.5) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  scale_color_manual(values = c("US" = "#2166AC", "PRC" = "#B2182B")) +
  labs(title = "VADER Compound Sentiment Over Time (RQ1.2)",
       subtitle = "Python VADER via reticulate | Triangulation with Bing",
       x = "Year", y = "Mean VADER Compound Score",
       color = "Corpus", size = "N Articles") +
  theme_minimal(base_size = 11)
```

# Part 6: Elective Extensions

## Deliverable 13–14: Quanteda Keyness (RQ3.1)

# Chi-squared keyness identifies words used significantly more in
# one corpus than the other. Accounts for corpus size imbalance
# (7,621 vs 5,391) via expected vs. observed frequencies.
# Viz: textplot_keyness, top 15 terms, blue=US, red=PRC.
```{r}
#| label: quanteda-dfm

library(text2vec)

qcorp <- corpus(sample_corpus, text_field = "fulltext",
                docid_field = "doc_id")

qtoks <- tokens(qcorp, remove_punct = TRUE, remove_numbers = TRUE) %>%
  tokens_tolower() %>%
  tokens_remove(c(stopwords("en"), custom_stops$word))

qdfm <- dfm(qtoks)

cat(sprintf("DFM dimensions: %d documents × %d features\n",
            nrow(qdfm), ncol(qdfm)))
```
```{r}
#| label: keyness

dfm_grouped <- dfm_group(qdfm, groups = corpus)
keyness_results <- textstat_keyness(dfm_grouped, target = "US")

textplot_keyness(keyness_results, n = 15,
                 color = c("#2166AC", "#B2182B")) +
  labs(title = "Keyness: U.S. vs. PRC Surveillance Vocabulary (RQ3.1)",
       subtitle = "Chi-squared test | Blue = U.S. | Red = PRC")
```

## Deliverable 15–16: GloVe Embeddings in R (RQ3.3, RQ4.2)

# Captures semantic relationships beyond frequency. Queries nearest
# neighbors for "surveillance" to see concept clustering.
# Technique: text2vec TCM + GlobalVectors, rank=50, window=5.
# With full data: train per-corpus and per-era models to measure
# semantic drift (RQ4.2).
```{r}
#| label: glove-embeddings

t2v_tokens <- sample_corpus$fulltext %>%
  tolower() %>%
  word_tokenizer()

it <- itoken(t2v_tokens, progressbar = FALSE)
vocab <- create_vocabulary(it) %>%
  prune_vocabulary(term_count_min = 3)
vectorizer <- vocab_vectorizer(vocab)
tcm <- create_tcm(it, vectorizer, skip_grams_window = 5L)

glove_model <- GlobalVectors$new(rank = 50, x_max = 10)
word_vectors <- glove_model$fit_transform(tcm, n_iter = 20,
                                           convergence_tol = 0.01)

cat(sprintf("GloVe embeddings: %d words × %d dimensions\n",
            nrow(word_vectors), ncol(word_vectors)))
```
```{r}
#| label: similar-words

if ("surveillance" %in% rownames(word_vectors)) {
  target_vec <- word_vectors["surveillance", , drop = FALSE]
  cos_sims <- sim2(x = word_vectors, y = target_vec,
                   method = "cosine", norm = "l2")
  nearest <- sort(drop(cos_sims[,1]), decreasing = TRUE)

  cat("Top 10 words most similar to 'surveillance':\n")
  print(head(names(nearest)[names(nearest) != "surveillance"], 10))
} else {
  cat("'surveillance' not in vocabulary (try with full corpus).\n")
}
```

## Deliverable 17: Word2Vec in Python (RQ3.3)

# Second embedding method for triangulation with GloVe.
# Technique: gensim Word2Vec skip-gram, dim=50, window=5.
# With full data: train per-corpus models, compare neighbors.
```{python}
#| label: word2vec

from gensim.models import Word2Vec
import math

corpus_data = r.sample_corpus

stop = set(__import__('nltk').corpus.stopwords.words("english"))
documents = []
for text in corpus_data['fulltext']:
    words = [w.lower() for w in str(text).split() if w.isalpha() and w.lower() not in stop]
    if words:
        documents.append(words)

model = Word2Vec(
    sentences=documents,
    vector_size=50,
    window=5,
    min_count=2,
    workers=1,
    sg=1,
    negative=10,
    epochs=10
)

kv = model.wv
print(f"Word2Vec vocab size: {len(kv)}")

def cosine_py(a, b):
    num = sum(x*y for x, y in zip(a, b))
    den = math.sqrt(sum(x*x for x in a)) * math.sqrt(sum(y*y for y in b))
    return (num / den) if den else 0.0

if "surveillance" in kv.key_to_index:
    q = kv.get_vector("surveillance").tolist()
    sims = []
    for w in kv.key_to_index.keys():
        if w == "surveillance":
            continue
        v = kv.get_vector(w).tolist()
        sims.append((w, cosine_py(q, v)))
    sims.sort(key=lambda x: x[1], reverse=True)
    print("\nWords most similar to 'surveillance' (Word2Vec):")
    for word, score in sims[:10]:
        print(f"  {word}: {score:.3f}")
```

# CRISP-DM Step 5: Evaluation

# Part 7: Publication Volume & Emotion Analysis (RQ4, RQ2.3)

## Deliverable 18: Article Volume Over Time (RQ4.1, RQ4.2)

# Tracks coverage volume as proxy for editorial attention.
# Volume spikes around events = initial evidence for RQ4.
# Viz: stacked area chart with event marker lines.
```{r}
#| label: volume-over-time

volume <- sample_corpus %>%
  count(year, corpus)

ggplot(volume, aes(x = year, y = n, fill = corpus)) +
  geom_area(alpha = 0.6, position = "stack") +
  geom_vline(xintercept = c(2001, 2013, 2017), linetype = "dotted",
             color = "gray30") +
  scale_fill_manual(values = c("US" = "#2166AC", "PRC" = "#B2182B")) +
  labs(title = "Publication Volume Over Time (RQ4.1, RQ4.2)",
       subtitle = "Stacked area | Dotted lines mark 9/11, Snowden, AI Era onset",
       x = "Year", y = "Number of Articles", fill = "Corpus") +
  theme_minimal(base_size = 11)
```

## Deliverable 19: NRC Emotion Analysis (RQ2.3)

# NRC lexicon classifies words into 8 emotions. Reveals which
# emotional frames dominate each corpus.
# Viz: grouped horizontal bar chart, US vs. PRC.
# Note: NRC license must be accepted interactively on first run.
```{r}
#| label: nrc-emotions
#| eval: false

# First run: accept NRC license interactively via get_sentiments("nrc")
# Then set eval: true

nrc <- get_sentiments("nrc") %>%
  filter(!sentiment %in% c("positive", "negative"))

emotion_counts <- tokens %>%
  inner_join(nrc, by = "word") %>%
  count(corpus, sentiment, sort = TRUE)

ggplot(emotion_counts, aes(x = reorder(sentiment, n), y = n, fill = corpus)) +
  geom_col(position = "dodge") +
  coord_flip() +
  scale_fill_manual(values = c("US" = "#2166AC", "PRC" = "#B2182B")) +
  labs(title = "NRC Emotion Profiles by Corpus (RQ2.3)",
       subtitle = "Which emotional frames dominate each corpus?",
       x = NULL, y = "Word Count", fill = "Corpus") +
  theme_minimal(base_size = 11)
```

# CRISP-DM Step 6: Deployment (Next Steps)

# Conclusion and Next Steps
#
# MVP Core (Completed):
#   - Word frequency (Deliverable 6) → RQ2.1
#   - Bigrams (Deliverable 7) → RQ2.1
#   - TF-IDF (Deliverable 8) → RQ2.1, RQ3.1
#   - Bing sentiment (Deliverables 9–11) → RQ1.1, RQ3.2, RQ4.1
#   - Data visualizations throughout
#
# Elective Extensions (In Progress):
#   - VADER sentiment (Deliverable 12) → RQ1.2
#   - Quanteda keyness (Deliverables 13–14) → RQ3.1
#   - GloVe embeddings (Deliverables 15–16) → RQ3.3, RQ4.2
#   - Word2Vec embeddings (Deliverable 17) → RQ3.3
#   - NRC emotion profiling (Deliverable 19) → RQ2.3
#
# Remaining for Final:
#   1. Add LDA topic modeling for RQ2.2 (test k = 5, 10, 15, 20)
#   2. Implement event-window analysis for RQ4.1 (12-month before/after)
#   3. Test multiple AI-era cutoffs (2015, 2017, 2019) for RQ4.2
#   4. Normalize comparative analyses for corpus size imbalance
#   5. Build GitHub repo for reproducibility


